Model LF

### 2022-11-05 max_dp endogen stød.Rmd
Commit

@@

plot(((nben_h_04 - nben_h_bs4) / nben_h_bs4), col= "black", xlab= "Year", ylab= "% changes in net benefits HH", main= "Net benefits HH");
lines(((nben_h_01 - nben_h_00) / nben_h_00), col= "red");
legend("left", legend=c("Scenario 3","Scenairo 1"),
       lty=c(1),lwd=c(2),bty="n", col = c("black","red"));
grid()
```

@@

@@

```{r}
plot(((yk_ds_05 - yk_ds_bs56) / yk_ds_bs56), col= "blue", xlab= "Year", ylab= "% Change in Gdp", main= "Gdp", ylim= c(-0.0011, 0.0015));
lines(((yk_ds_07b - yk_ds_bs7b) / yk_ds_bs7b), col= "red");
lines(((yk_ds_04 - yk_ds_bs4) / yk_ds_bs4), col= "yellow");
lines(((yk_ds_03 - yk_ds_bs3) / yk_ds_bs3), col= "black");
lines(((yk_ds_02 - yk_ds_bs2) / yk_ds_bs2), col= "orange");
lines(((yk_ds_01 - yk_ds_00) / yk_ds_00), col= "green");
legend("left", legend=c("All channels","All channels but productivity","Insurance rate channel", "Productivity channel", "Wage channel", "Demand channel"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue", "red","yellow", "black","orange", "green"));
grid()
```

```{r}
plot(((unemp_03 - unemp_bs3)*1000), col= "blue", xlab= "Year", ylab= "Change in Unemployment (people)", main= "Change in Unemployment");
lines(((unemp_05 - unemp_bs56)*1000), col= "black");
legend("left", legend=c("Productivity channel", "All channels"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue","black","red", "green"));
grid()
```

@@

**of all effects exept prod**

@@

>>>>

## Baseline Scenario 5b

```{r}
# Define add-factor list (defining shock)
constantAdjList_bs5b <- list(

 shock_kuld_model = TIMESERIES(shock_kuld_model_shock+1 ,START=c(2006,3),  FREQ='Q'),
  shock_wage_ds_model = TIMESERIES(shock_wage_ds_model_shock+1 ,START=c(2006,3),  FREQ='Q'),
 shock_prod_model = TIMESERIES(shock_prod_model_shock+1 ,START=c(2006,3),  FREQ='Q'),
 shock_lf_model = TIMESERIES(shock_lf_model_shock+1 ,START=c(2006,3),  FREQ='Q'),
 sens_3 = TIMESERIES(sens_3+1 ,START=c(2006,3),  FREQ='Q')

```{r}
# Simulate the model (following shock)
Shock_bs5b <- SIMULATE(S_model
                    ,simType='DYNAMIC'
                    ,TSRANGE=c(2006,3,2020,1)
                    ,simConvergence=0.00001
                    ,simIterLimit=100
                    ,ConstantAdjustment=constantAdjList_bs5b
                    )
```

```{r}
###Gengivelse af stød til model
max_dp_bs5b = Shock_bs5b$simulation$max_dp
wage_bs5b = Shock_bs5b$simulation$wage
komp_r_bs5b = Shock_bs5b$simulation$komp_r
part_bs5b = Shock_bs5b$simulation$part
yk_ds_bs5b = Shock_bs5b$simulation$yk_ds
pc_ds_bs5b = Shock_bs5b$simulation$pc_ds
wage_ds_t_bs5b = Shock_bs5b$simulation$wage_ds_t
ur_ds_bs5b = Shock_bs5b$simulation$ur_ds
emp_bs5b = Shock_bs5b$simulation$emp
yd_hk_ds_bs5b = Shock_bs5b$simulation$yd_hk_ds

tilpas_pr_bs5b = Shock_bs5b$simulation$tilpas_pr
u_ds_bs5b = Shock_bs5b$simulation$u_ds
part_bs5b = Shock_bs5b$simulation$part
nben_h_bs5b = Shock_bs5b$simulation$nben_h
wage_ds_bs5b = Shock_bs5b$simulation$wage_ds
dp_person_bs5b = Shock_bs5b$simulation$dp_person
kont_h_ratio_bs5b = Shock_bs5b$simulation$kont_h_ratio

nl_g_bs5b = Shock_bs5b$simulation$nl_g
unemp_bs5b = Shock_bs5b$simulation$unemp
yd_hk_ds_bs5b = Shock_bs5b$simulation$yd_hk_ds
wage_gap1_bs5b = Shock_bs5b$simulation$wage_gap1
wage_gap_bs5b = Shock_bs5b$simulation$wage_gap
prod_bs5b = Shock_bs5b$simulation$prod
```

@@

plot(((yd_hk_ds_04 - yd_hk_ds_bs4) / nben_h_bs4), col= "black", xlab= "Year", ylab= "% changes in disposable income", main= "Disposable income");
lines(((yd_hk_ds_01 - yd_hk_ds_00) / nben_h_00), col= "red");
legend("left", legend=c("Scenario 3","Scenairo 1"),
       lty=c(1),lwd=c(2),bty="n", col = c("black","red"));
grid()
```

@@

## Scenario 5b sens all

```{r}
# Define add-factor list (defining shock)
constantAdjList5b <- list(

  shock_reg_model = TIMESERIES(shock_reg_model_shock+1 ,START=c(2016,1),  FREQ='Q'),
 shock_wage_ds_model = TIMESERIES(shock_wage_ds_model_shock+1 ,START=c(2006,3),  FREQ='Q'),
 shock_prod_model = TIMESERIES(shock_prod_model_shock+1 ,START=c(2006,3),  FREQ='Q'),
 shock_kuld_model = TIMESERIES(shock_kuld_model_shock+1 ,START=c(2006,3),  FREQ='Q'),
 shock_lf_model = TIMESERIES(shock_lf_model_shock+1 ,START=c(2006,3),  FREQ='Q'),
 sens_3 = TIMESERIES(sens_3+1 ,START=c(2006,3),  FREQ='Q')

```{r}
# Simulate the model (following shock)
Shock_5b <- SIMULATE(S_model
                    ,simType='DYNAMIC'
                    ,TSRANGE=c(2006,3,2020,1)
                    ,simConvergence=0.00001
                    ,simIterLimit=100
                    ,ConstantAdjustment=constantAdjList5b
                    )

yk_ds_05b = Shock_5b$simulation$yk_ds
emp_05b = Shock_5b$simulation$emp
wage_ds_05b= Shock_5b$simulation$wage_ds
ur_ds_05b = Shock_5b$simulation$ur_ds
pc_ds_05b = Shock_5b$simulation$pc_ds
yd_hk_ds_05b = Shock_5b$simulation$yd_hk_ds
pconk_ds_05b = Shock_5b$simulation$pconk_ds
komp_r_05b = Shock_5b$simulation$komp_r
max_dp_05b = Shock_5b$simulation$max_dp
nben_h_05b = Shock_5b$simulation$nben_h
yd_hk_ds_05b = Shock_5b$simulation$yd_hk_ds
ik_05b = Shock_5b$simulation$ik
wage_ds_t_05b = Shock_5b$simulation$wage_ds_t
nben_h_un_05b = Shock_5b$simulation$nben_h_un
nl_g_05b = Shock_5b$simulation$nl_g
nsben_h_05b = Shock_5b$simulation$nsben_h
dp_person_05b = Shock_5b$simulation$dp_person
u_ds_05b = Shock_5b$simulation$u_ds
shock_kuld_05b = Shock_5b$simulation$shock_kuld
unemp_05b = Shock_5b$simulation$unemp

```{r}
plot((unemp_05b-unemp_bs5b)*1000, col= "red")
```

@@

```{r}
plot(((yk_ds_07b - yk_ds_bs7b) / yk_ds_bs7b), col= "blue", xlab= "Year", ylab= "% Change in Gdp", main= "Gdp", ylim= c(-0.0011, 0.0015));
lines(((yk_ds_04 - yk_ds_bs4) / yk_ds_bs4), col= "yellow");
lines(((yk_ds_02 - yk_ds_bs2) / yk_ds_bs2), col= "orange");
lines(((yk_ds_01 - yk_ds_00) / yk_ds_00), col= "green");
legend("top", legend=c("All channels but productivity","Insurance rate channel", "Wage channel", "Demand channel"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue","yellow","orange", "green"));
grid()
```

@@

**of all effects except prod**

@@

```{r}
plot(((unemp_03 - unemp_bs3)*1000), col= "blue", xlab= "Year", ylab= "Change in Unemployment (people)", main= "Change in Unemployment");
lines(((unemp_05 - unemp_bs56)*1000), col= "black");
lines(((unemp_s3_low-unemp_sbs3_low)*1000), col= "red");
lines(((unemp_05b-unemp_bs5b)*1000), col= "green");
legend("left", legend=c("Productivity channel",  "All channels", "Productivity channel sens", "All channels sens"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue","black","red", "green"));
grid()
```
